Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-08-20 latex/paper.tex
updated paper

@@

\subsubsection{Dinâmica}
Na rodada, são colocadas $2$ balas falsas e $1$ bala verdadeira na arma, sendo o player o primeiro a jogar. Ambos os jogadores podem escolher entre atirar em si mesmo, ou em seu oponente. Assim, a próxima ação é estritamente depende das probabilidades de ser uma bala real ou falsa. A partir dai, a dinâmica funciona da seguinte forma:

\begin{algorithm}[H]
	\begin{algorithmic}
		\If{jogador escolhe atirar no dealer}
			\If{bala for real}
				\State{Jogador ganha a rodada}
			\Else
				\State{Dealer joga a próxima}
			\EndIf
		\Else
			\If{bala for real}
				\State{Jogador perde}
			\Else
				\State{Player joga a próxima}
			\EndIf
		\EndIf

	\end{algorithmic}
	\caption{Possíveis jogadas}
	\label{alg:buckshot-roulette}
\end{algorithm}

Essa dinâmica se repete a cada jogada, sendo válida tanto para o dealer, como para o player.

\subsubsection{Versão clássica}
Para entender melhor a dinâmica, é possível representar cada ação e suas consequências em formato de árvore. Dessa forma, cada jogada leva a partida para mais próximo do fim.

\begin{center}
	\includegraphics[scale=0.2]{buckshot-roulette-diagram.png}
	\captionof{figure}{Buckshot Roulette diagrama de árvore}
	\label{fig:classical-model-bckr}
\end{center}

>>>>

\subsubsection{Game Dynamics}

In the first round, $2$ fake bullets and $1$ real are put into the shotgun. Then, the player starts his play, choosing between shooting himself or his opponent. If the player shoots himself and it's a real bullet, he loses one life point, otherwise he gets another chance to choose. However, if he chooses to shot his opponent, if it's real he takes away one life point from him, otherwise his opponent receives the gun.

This dynamics is followed in the entire game for both player and dealer, only being slight modified when power-ups are gained.

@@

\subsubsection{Modeling the Game Strategies}
The round dynamics can be modeled as a binary tree, using some game theory ideas to understand it better.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.2]{buckshot-roulette-diagram.png}
	\caption{Buckshot Roulette tree diagram}
	\label{fig:classical-model-bckr}
\end{figure}

For this diagram, it's expected that the player is a rational agent, which always plays aiming to win, and the dealer is a random agent, choosing randomly its decisions.
